\chapter{Source code guide}
\label{chap:Source code guide}

\section{Header files}
\label{sec:Header files}

The header files ({\tt *.h}) are located in {\tt src/include}. In {\tt DNA-functions.h}, the function prototypes are defined. The file {\tt DNA-constants.h} includes hash functions of constants (such as $\pi$) and mathematical operators (such as trigonometric functions or $\mathrm{min/max}$ operators). In the {\tt DNA.h} file, all structures used throughout the program are declared. There are four main structures, namely {\tt struct DNA\_RunOptions}, {\tt struct DNA\_FluidProperties}, {\tt struct DNA\_Fields} and {\tt struct DNA\_MovingBoundary}. The instances of these structures are created in {\tt main.c}. Their content, including nested structures, is as follows:

\begin{compactitem}
\item {\tt struct DNA\_RunOptions}: Structure containing variables and function pointers regarding the run options. Nested structures:
\begin{compactitem}
\item {\tt struct DNA\_NumericsFD}: Structure containing variables regarding the temporal and spatial discretization, such as $\Delta t$, $\Delta x$, etc., as well as function pointers associated with the boundary conditions. Nested structures:
\begin{compactitem}
\item {\tt struct DNA\_FDCoeffs}: Finite difference coefficients.
\end{compactitem}
\item {\tt struct DNA\_WaveExcitation}: Variables of the wave excitation functions (see Eqs. \eqref{eq:ExcitationSine} and \eqref{eq:GaussEnvelope}).
\item {\tt struct DNA\_Probes}: Variables specifying the acoustic pressure probes (see Sec. \ref{sec:Run options and fluid properties}).
\end{compactitem}
\item {\tt struct DNA\_FluidProperties}: Fluid properties such as the background density and speed of sound or the fluid nonlinearity.
\item {\tt struct DNA\_Fields}: Structure comprising all scalar fields. Nested structures:
\begin{compactitem}
\item {\tt struct DNA\_Grid}: Scalars and scalar fields representing the dependent coordinates $x\left(\xi,t\right)$ of the time-dependent physical domain $\Omega\left(t\right)$, the fixed computational domain $\Theta$, and the metrics of the coordinate transformation according to Eqs. \eqref{eq:linJacobian} to \eqref{eq:lindqdt}.
\item {\tt struct DNA\_ScalarField}: Several instances of this structure representing the field data such grid point coordinates, velocity fields, etc. Each of the individual scalar fields is an instance of this structure, which contains a pointer to the field.
\item {\tt struct DNA\_OldScalarFields}: Similar to the previous, but containing the data from the two preceding time steps. This information is needed for the time integration.
\end{compactitem}
\item {\tt struct DNA\_MovingBoundary}: Variables regarding the moving boundary of the physical domain $\Omega\left(t\right)$.
\end{compactitem}



\section{Source files}
\label{sec:Source files}

The core of the computational method evolves around solving the lossless convective Kuznetsov equation, Eq. \eqref{eq:convectiveKuznetsov}, however in the coordinates $\left(\xi,t\right)$ of the fixed computational domain $\Theta$. Therefore, the coordinate transformation is briefly repeated in Appx. \ref{chap:Appendix}. The following table provides an overview of the source files.

\noindent
\begin{longtable}{p{0.4\textwidth} p{0.55\textwidth}}
\textbf{Source file} & \textbf{Description}
\vspace{1mm} \\
\hline Directory {\tt include} &\\ \hline
{\tt DNA.h} & See Sec. \ref{sec:Header files}. \\
{\tt DNA-functions.h} & See Sec. \ref{sec:Header files}. \\
{\tt DNA-constants.h} & See Sec. \ref{sec:Header files}. \\
\\
\hline Directory {\tt io} &\\ \hline
{\tt ioreadoptionsfile.c} & Function that reads the {\tt wave-DNA} options file. \\
{\tt ioreadoneoption.c} & Called in {\tt ioreadoptionsfile.c} to read a single option the {\tt wave-DNA} options file. \\
{\tt ioreadcommandlineoptions.c} & Function to read command line options. \\
{\tt ioonscreen.c} & Functions for output on screen during the run time of the simulation. \\
{\tt iodefaultoptions.c} & Defaults for the options that can be set in the {\tt wave-DNA} options file. A simulation is performed even with an empty options file (see Sec. \ref{sec:Default run}). \\
{\tt ioresults.c} & Functions to write ouput data to disk. \\
\\
\hline Directory {\tt initialize} &\\ \hline
{\tt initializesimulation.c} & Routine that allocates memory for all scalar fields and results vectors by calling functions in {\tt memoryallocfields.c} (see below). Initial values are set and the grid point IDs corresponding to the coordinates of the probe sample locations (IDs of the nearest neighbours are taken) specified in the {\tt wave-DNA} options file are identified. \\
{\tt initializeprocessoptions.c} & Setting all function pointers based on the specifications in the {\tt wave-DNA} options file or the default options. \\
{\tt initializefield.c} & Routines to initialize single fields of the type {\tt struct DNA\_ScalarField} or {\tt struct DNA\_OldScalarFields}. \\
\\
\hline Directory {\tt memory} &\\ \hline
{\tt memoryalloc.c} & Function to allocate memory (RAM) for fields of the types {\tt struct DNA\_ScalarField} or {\tt struct DNA\_OldScalarFields}, for the computational grid, and the probe sample points and vecotrs. \\
{\tt memoryallocfields.c} & Routine calling {\tt memoryalloc.c} to allocate all fields. \\
{\tt memoryfreefields.c} & Routine called in {\tt main.c} to free all fields upon termination of the prgramme. \\
\\
\hline Directory {\tt grid} &\\ \hline
{\tt gridmakegrid.c} & Functions to create the time-dependent grid for the physical domain $\Omega\left(t\right)$ and the fixed grid for the computational domain $\Theta$. \\
{\tt gridmotion.c} & Updating the derivatives of the dependent coordinate $\xi\left(r,t\right)$ as given by by Eqs. \eqref{eq:linJacobian} to \eqref{eq:lindqdt}. \\
\\
\hline Directory {\tt fd} &\\ \hline
{\tt fdcoeffs.c} & Finite difference coefficients for the spatial and temporal discretization. \\
{\tt fddx.c} & Functions to construct the explicit finite difference approximations of the spatial derivatives.  \\
{\tt fddt.c} & Functions to construct the explicit finite difference approximations of the time derivatives. \\
{\tt fdsumay.c} & Functions to compute the sums over previous time-steps needed for the finite difference discretiztion (see Eq. \eqref{eq:fddt_compact}). \\
{\tt fdboundaryconditions.c} & Functions to apply the boundary conditions. The functions for the West and East boundaries are called by reference. The corresponding pointers are {\tt int (*FDBC\_West)(...)} and {\tt int (*FDBC\_East)(...)}, respectively.  \\
\\
\hline Directory {\tt waveexcitation} &\\ \hline
{\tt waveexcitation.c} & Functions to excite the acoustic pressure wave at the specified excitation node. \\
\\
\hline Directory {\tt boundary} &\\ \hline
{\tt boundarymotion.c} & Functions to describe the motion of the moving domain boundary. \\
{\tt boundaryconditions.c} & Calling the functions to set the boundary conditions. \\
\\
\hline Directory {\tt backgroundflow} &\\ \hline
{\tt backgroundflowmotion.c} & Functions to compute the background flow velocity field $u_0$ and its spatial and temporal derivatives. \\
{\tt backgroundflowgravitation.c} & Function to compute the gravitational potential if applicable. \\
\\
\hline Directory {\tt transform} &\\ \hline
{\tt transformeqn.c} & Functions to compute the space- and time-dependent coefficients of the transformed wave equation, Eq. \eqref{eq:convectiveKuznetsov_BBB}  and to assemble the terms of the discretized equation. The file contains the function {\tt TransformEqn\_Predictor} to assemble the terms for the predictor step of the predictor-corrector method (see Eq. \eqref{eq:discreteEqn}), and the function {\tt TransformEqn\_Corrector}, which only updates the coefficients and terms that are relevant for the corrector step (see Eq. \eqref{eq:corrector}).\\
{\tt transformpotential.c} & Routines to convert the acoustic pressure $p_1$ into the perturbation potential $\Phi_1$ (needed at the excitation node) and vice versa (needed to reconstruct the acoustic pressure field from the solution for $\Phi_1$). \\
{\tt transformgeometricaldecay.c} & Function to account for the change of the cross-sectional area $A$ in the Laplacian (see Eq. \eqref{eq:convectiveKuznetsov}) in the case of spherical symmetry. \\
\\
\hline Directory {\tt solve} &\\ \hline
{\tt solveloop.c} & This file contains the function {\tt SolveTimeLoop}, representing the time loop of the simulation, and the function {\tt Solve}, which is called in {\tt {\tt SolveTimeLoop}} at each time step and which calls the functions relevant to the numerical algorithm. \\
{\tt solveexplicitderivatives.c} & Routine calling the functions in {\tt fddx.c} and {\tt fddt.c} to construct the finite difference approximations explicit temporal, spatial, and mixed derivatives. \\
{\tt solvesumay.c} & Routine calling the functions in {\tt fdsumay.c} to compute the sums over the previous time steps needed for the explicit finite difference approximations of the time-derivatives. \\
{\tt solveupdatefields.c} & Contains the function that updates the old fields and the term $\Phi_1\partial \xi/\partial t$ in Eq. \eqref{eq:mixedTerm}. \\
{\tt solvepredictorcorrector.c} & Routines to apply the predictor (see Eq. \eqref{eq:discreteEqn}) and the corrector steps (see Eq. \eqref{eq:corrector}). Additional routines are to update the Laplacian prior to the corrector step and to store the initial guess $\widetilde{\Phi_{1,i}}$ computed based on Eq. \eqref{eq:discreteEqn} and needed in Eq. \eqref{eq:corrector}. \\
 \hline
\end{longtable} \vspace{1em}

